\documentclass[12pt,a4paper]{article}
\usepackage[finnish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{charter}  % font

\usepackage{fixltx2e}  % \textsubscript

\usepackage[chordbk]{songbook}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.0in}
\addtolength{\hoffset}{-0.3in}
\addtolength{\textwidth}{1.5in}

\begin{document}
\thispagestyle{empty}
\section*{Ruusupuu}

\SBIntro{\Ch{Dm}{\SBLyricNoteFont Juuson soolo} \Ch{C}{} \Ch{Dm}{}}

\begin{SBVerse}
\Ch{F}{Pidän} vanhemmista \Ch{G}{naisista.} \Ch{F}{On} niiden kanssa helppoo
\Ch{Em}{jutella.}

\Ch{F}{Ne} raahaa jotain \Ch{G}{mammuttia} \Ch{F}{Sepänkadun}
sillal\Ch{Em}{la.}

\Ch{F}{Se} on meno\Ch{G}{ssa} \Ch{F}{Turusta} Ouluun kuulem\Ch{Em}{ma.}

\Ch{F}{Onko} täällä \Ch{G}{enää} \Ch{F}{ystävyyttä} missään \Ch{Em}{muodossa?}
\end{SBVerse}

\begin{SBChorus}
\Chr{Dm}{Ruusu}\Ch{Bb}{puu} ja mi\Ch{F}{nä} \Ch{A}{}
\Chr{Dm}{seiso}\Ch{Bb}{taan} kestävi\Ch{F}{nä} \Ch{A}{}

\Chr{Dm}{maail}\Ch{Bb}{massa,} jossa \Ch{F}{kaivaa} \Ch{A}{saa}
\Chr{Dm}{rakka}\Ch{Bb}{utta} esiin \Ch{F}{} \Chr{A}{katepillaril}\Ch{Dm}{la.}
\end{SBChorus}

\begin{SBVerse*}
\Ch{Dm}{\SBLyricNoteFont Juuson soolo} \Ch{C}{} \Ch{Dm}{}
\end{SBVerse*}

\begin{SBVerse}
\Ch{F}{Puhun} puhelimes\Ch{G}{sa} \Ch{F}{jälleen} tuntitolkul\Ch{Em}{la.}

\Ch{F}{Kai} se on tärke\Ch{G}{ää,} \Ch{F}{ettei} menettäisi hän
järke\Ch{Em}{ään.}

\Ch{F}{Onko} pimeyden keskel\Ch{G}{lä} \Ch{F}{valon} pilkahduksi\Ch{Em}{a?}

\Ch{F}{Onnen} kyyne\Ch{G}{leitä,} \Ch{F}{ilon} kiljahduksi\Ch{Em}{a?} (onko?)
\end{SBVerse}

\begin{SBChorus}
\Chr{Dm}{Ruusu}\Ch{Bb}{puu} ja mi\Ch{F}{nä} \Ch{A}{}
\Chr{Dm}{seiso}\Ch{Bb}{taan} kestävi\Ch{F}{nä} \Ch{A}{}

\Chr{Dm}{maail}\Ch{Bb}{massa,} jossa \Ch{F}{kaivaa} \Ch{A}{saa}
\Chr{Dm}{rakka}\Ch{Bb}{utta} esiin \Ch{F}{} \Chr{A}{katepillaril}\Ch{Dm}{la.}

Ruusu\Ch{Bb}{puu} ja mi\Ch{F}{nä} \Ch{A}{} \Chr{Dm}{seisot}\Ch{Bb}{tiin}
kestävi\Ch{F}{nä,} \Ch{A}{}

\Ch{Dm}{kunnes} \Ch{Bb}{puu} tuo kaadet\Ch{F}{tiin,} \Ch{A}{} \Ch{Dm}{maahan}
\Chr{Bb}{haudat}\Ch{F}{tiin} \Chr{A}{katepilla}\Ch{Dm}{rilla.}
\end{SBChorus}

\begin{SBVerse*}
\Ch{Dm}{\SBLyricNoteFont Maken soolo} \Ch{Bb}{} \Ch{F}{} \Ch{A}{} \Ch{Dm}{}
\Ch{Bb}{} \Ch{F}{} \Ch{A}{} \Ch{Dm}{} \Ch{Bb}{} \Ch{F}{} \Ch{A}{} \Ch{Dm}{}
\Ch{Bb}{} \Ch{F}{} \Ch{A}{}
\end{SBVerse*}

\SBEnd{\Chr{Dm}{}}

{\SBLyricNoteFont Johan: P\textsubscript{2}16~Or:Emerson, scene~1+2, kertsissä
mod$\uparrow$ ja kahdella oktaavilla.}

\end{document}
